Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-15 writeup/gz_hubble_data.tex

Include cookbook for selecting morphologies.

Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2.

@@

Summarize the broad trends that are seen regarding the fraction of galaxies with various morphologies, how that relates to color, size, etc. Briefly discuss results as compared with literature and theory.

>>>>

The intended purpose of the GZH catalog is to provide a simple, yet flexible, means of identifying samples of galaxies with a desired morphological type. Here we provide instructions for creating such samples using the vote fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}. We stress that the selection process will vary based on the particular science case.

To select galaxies of a morphological type identified with a Task offered in the decision tree (see Figure~\ref{fig:decisiontree}, a cut is placed on the vote fraction for that Task ($p_{\rm task}$), as well as the vote fractions for the Tasks preceding it. For example, to select barred galaxies, a cut may be placed on $p_{\rm bar}$ such that only galaxies where a high fraction of votes for this task voted for the $bar,yes$ answer. This is not the only necessary cut, however, since not all users answer this question; only those who have previously selected ``features'' in Task~01, ``not clumpy'' in Task~12, and ``not edge-on'', \emph{or} previously selected ``features'' in Task~01, ``clumpy'' in Task~12, ``$>$ 2 clumps'' in Task~16, and ``spiral arrangement'' in Task~15 will have the opportunity to vote on the bar question, Task~03. To ensure that $p_{\rm bar}$ is well-sampled, cuts on all previous tasks must be applied.

The flexibility of this catalog allows the user to set their own selection criteria for vote fraction thresholds to create a morphologically-pure sample. In Table~\ref{tab:prev_tasks} we offer baseline cuts for selecting galaxies of a variety of morphologies. {\note As an example: to select barred galaxies, one should select objects with $p_{\rm features}>0.52, p_{\rm clumpy,no} > 0.55,$ and $p_{edgeon,no}>x.xx$ \emph{or} objects with $p_{\rm features}>0.52, p_{\rm clumpy,yes} > x.xx, (p_{\rm clump~count, 3}+p_{\rm clump~count,4}+p_{\rm clump~count,>4}+p_{\rm clump~count,can't~tell})>x.xx,$ and $p_{\rm clump~arrangement,spiral}>x.xx.$} These cuts define a sample of galaxies of ``bar candidates''; ie galaxies for which answering the bar question makes physical sense and the vote fraction $p_{\rm bar}$ is well-sampled. In this example, such galaxies are featured, non-clumpy, non-edge~on galaxies, or featured, clumpy, spiral galaxies. At this point a cut can be made on $p_{\rm bar}$ to select a clean sample of only strong bars $p_{\rm bar}>0.8$, or a complete sample of weak and strong bars $p_{\rm bar}>0.3$, or the value most appropriate to the science case.

{\note
\begin{itemize}
    \item explain decision tree format; vote fractions are dependent on previous task vote fractions
    \item provide example of how to select bars
    \item discuss difference between conservative/clean sample and loose/complete sample, emphasize goals differ depending on science case
\end{itemize}
}

\begin{table*}
\caption{Cookbook \label{tab:prev_tasks}}
\begin{tabular}{llll}
\hline\hline
Task No. &  Task 	        & Previous Task  & Vote Fraction Cut \\
         &            	        &                & $N_{task} \ge 20$ \\
\hline
01       & smooth or features   &  -                  & -                 \\
02       & edge on              & 01, 12              & $p_{\rm clumpy,no}>0.55$              \\
03       & bar		            & 01, 12, 02          & $p_{\rm edgeon,no}>$                 \\
         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
04       & spiral arms          & 01, 12, 02          & $p_{\rm edgeon,no}>$                  \\
         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
05       & bulge prominence     & 01, 12, 02          & $p_{\rm edgeon,no}>$                 \\
         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
06       & odd yes/no           & -                   &                   \\
07       & rounded              & 01                  & $p_{\rm smooth}>0.45$               \\
08       & odd feature          & 06                  & $p_{\rm odd,yes}>$                  \\
09       & bulge shape          & 01, 12, 02          & $p_{\rm edgeon,yes}>$               \\
10       & arms winding         & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                  \\
         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
11       & arms number          & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                 \\
         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
12       & clumpy               & 01                  & $p_{\rm features}>0.52$              \\
13       & bright clump         & 01, 12, 16          & $p_{\rm one clump}<$                 \\
14       & bright central clump & 01, 12, 16, 13      & $p_{\rm bright clump,yes}>$           \\
15       & clump arrangement    & 01, 12, 16          & $p_{\rm one clump}<$                \\
16       & clump count          & 01, 12              & $p_{\rm clumpy,yes}>0.55$              \\
17       & clumps symmetrical   & 01, 12, 16          & $p_{\rm one clump}<$                \\
18       & clumps embedded      & 01, 12, 16          &  $p_{\rm one clump}<$                 \\

\hline\hline
\end{tabular}
\end{table*}

@@

{\note \it Summarize the broad trends that are seen regarding the fraction of galaxies with various morphologies, how that relates to color, size, etc. Briefly discuss results as compared with literature and theory.}
